### 2016-06-24 sec1_introduction.tex
Commit first
Updates on Experiments Graphs
Revise Sec 5 last portion and Appendix
Lets fix sec 6!!
aaaaa
An almost finished version
Continue to revise

%It is easy to spot that none of the existing solutions are scalable to handle large-scale trajectories which include near billions of data points.
%In fact, as shown in Table~, the mining of co-movement patterns require high complexity. For instance, the
%complexities of \emph{swarm} and \emph{platoon} are already exponential. 
%Therefore, none of them can handle millions of trajectories efficiently. 
%CAN YOU ANALYSE THEIR COMPLEXITY TO ADDRESS THE PROBLEM OF SCALABILITY.
\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_O.eps}
		\subcaption{$1k$ timestamps}
    \label{fig:fig1}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_T.eps}
         \subcaption{$1k$ objects}
    \label{fig:fig2}
    \end{subfigure}
    \caption{Performance measures on existing co-movement patterns. A sampled Geolife data set
    is used with up two 2.4 million data points. Default parameters are $M=10$ $K=20$ $L=10$.}
    \label{fig:related_work_scalability}
\end{figure}

@@

Second, we investigate deploying our GCMP detector on MapReduce platforms (such as Hadoop and Spark) to tackle the scalability issue. Our technical contributions are three-fold. First, we replicate the snapshots in multiple data chunks to support efficient parallel processing. Second, we devise a novel \emph{Star Partition and Mining} (SPM) algorithm as a fine-granularity partitioning strategy to achieve workload balance. For each star, an Apriori method is adopted to mine the co-movement patterns. Third, we leverage the \emph{temporal monotonicity} property of GCMP to design several optimization techniques including \emph{edge-simplification} to prune initial candidates, \emph{temporal apriori pruning} and \emph{forward closure checking} to reduce the number of enumerated candidates in the Apriori algorithm.
%
%we propose two types of optimization techniques to further improve the performance, including \emph{edge-simplification} to boost the shuffle process and \emph{temporal monotonicity pruning} and 
%\emph{forward closure checking} to significantly reduce the number of enumerated candidates in the Aproiro algorithm.

We conduct a set of extensive experiments on three large-scaled real datasets with hundreds of millions 
temporal points. 
The results show that our parallel scheme efficiently supports GCMP mining in large datasets.
In particular, with near 200 million trajectory points, 
our scheme runs within 10 minutes using 135 cores. Whereas centralized solution takes near 7 hours for 
1 million trajectory points.
Moreover, our optimized SPM methods achieves upto XXX times efficiency
as compared to the baseline algorithm with near linear scalability.

The rest of our paper is organized as follows: Section~\ref{sec:related_works} summarizes the relevant literature on 
trajectory pattern mining. Section~\ref{sec:definition} states the problem definition of our general co-movement pattern mining. Section~\ref{sec:trm} provides a baseline solution. An advanced solution named
\emph{star partition and mining} is presented in Section~\ref{sec:spm}. Section~\ref{sec:opt} discusses various optimization techniques. Section~\ref{sec:exp} conducts extensive experiments to verify the efficiency of our system. Finally Section~\ref{sec:concl} concludes the paper.

>>>>

%It is easy to spot that none of the existing solutions are scalable to handle large-scale trajectories which include near billions of data points.
%In fact, as shown in Table~, the mining of co-movement patterns require high complexity. For instance, the
%complexities of \emph{swarm} and \emph{platoon} are already exponential. 
%Therefore, none of them can handle millions of trajectories efficiently. 
%CAN YOU ANALYSE THEIR COMPLEXITY TO ADDRESS THE PROBLEM OF SCALABILITY.
\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_O.eps}
		\subcaption{$1k$ timestamps}
    \label{fig:fig1}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_T.eps}
         \subcaption{$1k$ objects}
    \label{fig:fig2}
    \end{subfigure}
    \caption{Performance measures on existing co-movement patterns. A sampled Geolife data set
    is used with up two 2.4 million data points. Default parameters are $M=15$ $K=180$ $L=30$.}
    \label{fig:related_work_scalability}
\end{figure}

@@

Second, we investigate deploying our GCMP detector on MapReduce platforms (such as Hadoop and Spark) to tackle the scalability issue. Our technical contributions are three-fold. First, we replicate the snapshots in multiple data chunks to support efficient parallel processing. Second, we devise a novel \emph{Star Partition and ApRiori Enumerator} (SPARE) framework as a fine-granularity partitioning strategy to achieve workload balance. For each star, an Apriori Enumerator is adopted to mine the co-movement patterns. Third, we leverage the \emph{temporal monotonicity} property of of GCMP 
to design several optimization techniques including \emph{sequence simplification}, \emph{monontonicity pruning} and \emph{forward closure check} to further reduce the number of candidates enumerated.
%
%we propose two types of optimization techniques to further improve the performance, including \emph{edge-simplification} to boost the shuffle process and \emph{temporal monotonicity pruning} and 
%\emph{forward closure checking} to significantly reduce the number of enumerated candidates in the Aproiro algorithm.

We conduct a set of extensive experiments on three large-scaled real datasets with hundreds of millions 
temporal points. 
The results show that both our parallel scheme efficiently supports GCMP mining in large datasets.
In particular, with near 200 million trajectory points, 
SPARE runs in 15 minutes using 172 cores. Whereas
centralized solutions take near 7 hours 
for 1 million trajectory points.
Moreover, our optimized SPARE methods achieves upto 10 times efficiency
as compared to the baseline algorithm with almost linear scalability.

The rest of our paper is organized as follows: Section~\ref{sec:related_works} summarizes the relevant literature on 
trajectory pattern mining. Section~\ref{sec:definition} states the problem definition of our general co-movement pattern mining. Section~\ref{sec:trm} provides a baseline solution. An advanced solution named
\emph{star partition and mining} is presented in Section~\ref{sec:spm}. Section~\ref{sec:exp} conducts extensive experiments to verify the efficiency of our system. Finally Section~\ref{sec:concl} concludes the paper.
